Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-06 docs/evol.tex
improved writing

Although there seems to be zero tendency taken over all versions of
all projects together, the situation might be different in individual
projects. We therefore performed Spearman correlations between bug
counts and version ordinals in all projects we examined. These paint a
different picture from the above table, shown in
Figure~\ref{fig:bugsversionscorr}. The spike in point zero is explained
by the large number of projects for which no correlation could be
established---note that the scale is logarithmic.

But we can see that there were projects where a correlation could be
established, either positive or negative. The {\it Security High}
category is particularly bimodal, but this is explained by the small
number of correlations that could be established, nine in total. Taken
together with Table~\ref{tbl:bugsperversion} this suggests that: we
cannot say that across projects defect counts increase or decrease
significantly across time. But in individual projects, defect counts
can have a strong upwards or downwards tendency. There may be no such
thing as a ``project'' in general, only particular projects with their
own idiosyncrasies, quality features, and coding practices.

>>>>

Although there seems to be zero tendency taken over all versions of
all projects together, the situation might be different in individual
projects. We therefore performed Spearman correlations between bug
counts and version ordinals in all projects we examined. These paint a
different picture from the above table, shown in
Figure~\ref{fig:bugsversionscorr}. The spike in point zero is
explained by the large number of projects for which no correlation
could be established---note that the scale is logarithmic. Still, we
can see that there were projects where a correlation could be
established, either positive or negative. The {\it Security High}
category is particularly bimodal, but this is explained by the small
number of correlations that could be established, nine in total. Taken
together with Table~\ref{tbl:bugsperversion},
Figure~\ref{fig:bugsversionscorr} suggests that we cannot say that across
projects defect counts increase or decrease significantly across time.
In individual projects, however, defect counts can have a strong
upwards or downwards tendency. There may be no such thing as a
``project'' in general, only particular projects with their own
idiosyncrasies, quality features, and coding practices.
